Weather Data Integration and Assimilation System\\

### 2020-02-21 Paper.tex
Paper: fixed table width

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[acronym]{glossaries}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{biblatex}

@@

\begin{itemize}
    \item \textbf{Module ID} -  String field which describe the source of the data generated.
    \item \textbf{Value Type} -  Scalar, Vector, Grid type
    \item \textbf{Location} - Location of the timeseries. Point location, regular grid location or irregular grid location.
    \item \textbf{Parameter} - variable measuring against a location
    \item \textbf{Timeseries Type} - Such as Historical or forecast
    \item \textbf{Time Step} - Unit of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance. One of multiplier or divider can be used to define the interval between each measurement.
\end{itemize}

@@

The test plan is to perform load testing on whole system, and analyze the scalability of the system while measuring the operations perform on each module. Two variables can vary while doing performance testing.
\begin{enumerate}
    \item Number of requests made to the system at a given time (\acrfull{rps})
    \item Request size
\end{enumerate}

@@

\begin{table}[ht]
\centering
\caption{\acrshort{eks} nodes}
\footnotesize
\begin{tabular}{|l|c|c|c|c|l|}
\hline
\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\label{ptab:aws_eks_nodes}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Evaluation}
\label{psubse:performance_evaluation}
\begin{table}[htbp]
\caption{Table type styles}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{Std} & \textbf{90\% Line} \\ \hline
Insert Scalar & 71727 & 34 & 13 & 1777 & 118.78 & 27 \\ \hline
Retrieve Scalar & 71693 & 7 & 5 & 1608 & 18.72 & 9 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 14.07 & 98 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 37.79 & 110 \\ \hline
Query & 71704 & 1 & 0 & 203 & 2.05 & 2 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 212.35 & 501 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, Std: Standard Deviation.}
\end{tabular}
\label{ptab:obs_all_auto_15_min_summary_latency}
\end{center}
\end{table}

\begin{table}[htbp]
\caption{Table type styles}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Std. Dev.} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Scalar & 71727 & 34 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Vector & 71693 & 7 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 37.79 & 0.00\% & 4.5 \\ \hline
Query & 71704 & 1 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 212.35 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency.}
\end{tabular}
\label{ptab:obs_all_auto_15_min_summary_throughput}
\end{center}
\end{table}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[acronym]{glossaries}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{biblatex}
\usepackage{adjustbox}

@@

\begin{itemize}
    \item \texttt{Module ID}--  String field which describe the source of the data generated.
    \item \texttt{Value Type}--  Scalar, Vector, Grid type
    \item \texttt{Location}-- Location of the timeseries. Point location, regular grid location or irregular grid location.
    \item \texttt{Parameter}-- variable measuring against a location
    \item \texttt{Timeseries Type} - Such as Historical or forecast
    \item \texttt{Time Step}-- Unit of Second, Minute, Hour, Day, Week, Month, Year, or NonEqualDistance. One of multiplier or divider can be used to define the interval between each measurement.
\end{itemize}

@@

The test plan is to perform load testing on whole system, and analyze the scalability of the system while measuring the operations perform on each module. Two variables can vary while doing performance testing.
\begin{enumerate}
    \item \acrfull{rps}
    \item Request size
\end{enumerate}

@@

\begin{table}[ht]
\centering
\caption{\acrshort{eks} nodes}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|l|c|c|c|c|l|}
\hline
\textbf{Node Label} & \textbf{vCPU} & \textbf{RAM (GB)} & \textbf{Storage (GB)} & \textbf{Quantity} & \textbf{EC2 Name} \\ \hline
core & 16 & 32 & 15 & 1 & c5.4xlarge \\ \hline
grid & 8 & 16 & 25 & 1 & c5.2xlarge \\ \hline
scalar & 8 & 16 & 20 & 1 & c5.2xlarge \\ \hline
test & 4 & 10.5 & 5 & 1 & c5n.xlarge \\ \hline
\end{tabular}
\end{adjustbox}
\label{ptab:aws_eks_nodes}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Evaluation}
\label{psubse:performance_evaluation}

While performing the load testing, each test plan performed around 310k of total sample requests within 30minutes. The ratio between Scalar and Vector to Grid operations around 71k:8k with the ratio of 90\%:10\%. This implies that test cases were able to perform as planned in the \cref{psubse:test_plan}. Insert

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 60min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71826 & 28 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_60_min_summary_throughput}
\end{center}
\end{table}

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 30min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71759 & 29 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 207.10 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_30_min_summary_throughput}
\end{center}
\end{table}

\begin{table}[htbp]
\caption{ Throughput and Latency of load testing with 15min data}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71775 & 30 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_15_min_summary_throughput}
\end{center}
\end{table}

\begin{table}[htbp]
\caption{Throughput and Latency of load testing with 15min data while enabled K8s
auto-scaling}
\begin{center}
\begin{adjustbox}{width=0.45\textwidth}
\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg$^{\mathrm{a}}$} & \textbf{90\%$^{\mathrm{b}}$} & \textbf{S.D.$^{\mathrm{c}}$} & \textbf{Error \%} & \textbf{RPS} \\ \hline
Insert Timeseries & 71727 & 34 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Avg: Average Latency, $^{\mathrm{b}}$S.D.: Standard Deviation, $^{\mathrm{c}}$90\%: 90\% percentile.}
\end{tabular}
\end{adjustbox}
\label{ptab:obs_all_auto_15_min_summary_throughput}
\end{center}
\end{table}

### 2020-02-21 results/sec_2-workload.tex
Paper: fixed table width

Almost similar to how was the precipitation data proceed, the water level is prepared for Grid data. One exception with Grid data during these test cases was, the maximum time step is 30min, instead of 15min due to the larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide an extensible architecture framework, during the performance testing it is not much considered about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extent.

>>>>

Almost similar to how was the precipitation data proceed, the water level is prepared for Grid data. The Grid data files are real data output of FLO2D 150 meter hydrology model which uses in the \acrshort{curw}. Each file follow the format of ASCII Grid file and consist of 120 rows and 139 columns with using the \texttt{-9} for the missing data as an optimization. Each file size is 50,337 Bytes (50 Kilobytes).
% One exception with Grid data during these test cases was, the maximum time step is 30min, instead of 15min due to the larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide an extensible architecture framework, during the performance testing it is not much considered about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extent.

### 2020-02-21 results/sec_3-observations.tex
Paper: fixed table width

According to \cref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in \cref{se:workload}.

Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling auto-scaling as explained in \cref{subse:test_plan_metrics} for high resource utilized microservice.

@@

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the requests are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller. Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms. Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ration in \cref{se:test_plan}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Load testing with hourly data - Response Time vs Threads}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads. As the graph shows, the response time kept the same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias} since the system able to process more requests without a significant change in the latency. When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data.

>>>>

According to \cref{se:test_plan} section, This section includes the observations based one the test plans in \cref{se:test_plan} and test plan test up which is explained in \cref{se:workload}. Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes data (24 data points), 30 minutes data (48 data points) and 15 minutes data (96 data points) by variate the request size. Then another performance test with enabling auto-scaling for the higher resource utilized microservices as explained in \cref{subse:test_plan_metrics}.

@@

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the requests are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} for Scalar and Vector data with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries is similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the requests perform within the same amount of time, hence the standard deviation is smaller. The delay in inserting Grid timeseries smaller because those requests are handling asynchronously. Retrieve Grid Timeseries data perform the same but with a bit higher value of latency of 68ms. Both insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only gets 10\% of the number of requests per given time via the test plan as explained in the data ratio in \cref{se:test_plan}.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Load testing with hourly data - Response Time vs Threads}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads. As the graph shows, the response time kept the same while increasing the number of active threads against each test case. This shows the scalability of the \acrshort{wdias} since the system able to process more requests without a significant change in the latency. When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving Scalar and Vector data. This is because of those data handle on demand and depend on the timeseries database performance.
